Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-25 sections/appendix.tex
no parens

>>>>

\section{Mask Images}
We interpreted the following images from ``Digital Image Processing'' \cite{gonzalez_digital_2006} as masks:

\textbf{FigP1012.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP1012.png}}

\textbf{Fig1008\_a\_\_step edge\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1008\_a\_\_step edge\_.png}}

\textbf{FigP0905\_d\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_d\_.png}}

\textbf{FigP0528\_c\_\_doughnut\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0528\_c\_\_doughnut\_.png}}

\textbf{FigP0616\_b\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0616\_b\_.png}}

\textbf{Fig0114\_c\_\_bottles\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0114\_c\_\_bottles\_.png}}

\textbf{FigP0616\_c\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0616\_c\_.png}}

\textbf{FigP0433\_b\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0433\_b\_.png}}

\textbf{Figp0917.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Figp0917.png}}

\textbf{FigP0905\_b\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_b\_.png}}

\textbf{Fig1059\_c\_\_NegADI\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1059\_c\_\_NegADI\_.png}}

\textbf{Fig1111\_a\_\_triangle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1111\_a\_\_triangle\_.png}}

\textbf{Fig1111\_b\_\_square\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1111\_b\_\_square\_.png}}

\textbf{FigP0905\_top\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_top\_.png}}

\textbf{FigP1110.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP1110.png}}

\textbf{Fig0533\_a\_\_circle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0533\_a\_\_circle\_.png}}

\textbf{FigP0917\_noisy\_rectangle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0917\_noisy\_rectangle\_.png}}

\textbf{Fig0230\_b\_\_dental\_xray\_mask\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0230\_b\_\_dental\_xray\_mask\_.png}}

\textbf{FigP0528\_b\_\_two\_dots\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0528\_b\_\_two\_dots\_.png}}

\textbf{Fig1059\_a\_\_AbsADI\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1059\_a\_\_AbsADI\_.png}}

\textbf{Fig1059\_b\_\_PosADI\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1059\_b\_\_PosADI\_.png}}

\textbf{Fig0539\_c\_\_shepp-logan\_phantom\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0539\_c\_\_shepp-logan\_phantom\_.png}}

\textbf{FigP0905\_c\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_c\_.png}}

\textbf{Fig1043\_a\_\_yeast\_USC\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1043\_a\_\_yeast\_USC\_.png}}

\textbf{FigP0905\_U\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_U\_.png}}

\textbf{Fig0524\_b\_\_blurred-impulse\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0524\_b\_\_blurred-impulse\_.png}}

\textbf{Fig0424\_a\_\_rectangle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0424\_a\_\_rectangle\_.png}}

\textbf{Fig1008\_c\_\_roof\_edge\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1008\_c\_\_roof\_edge\_.png}}

\textbf{Fig0539\_a\_\_vertical\_rectangle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0539\_a\_\_vertical\_rectangle\_.png}}

\textbf{FigP0905\_a\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0905\_a\_.png}}

\textbf{FigP0433\_a\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0433\_a\_.png}}

\textbf{Fig0.15\_a\_\_translated\_rectangle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0425\_a\_\_translated\_rectangle\_.png}}

\textbf{FigP0918\_c\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0918\_c\_.png}}

\textbf{Fig0524\_a\_\_impulse\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0524\_a\_\_impulse\_.png}}

\textbf{Fig0236\_a\_\_letter\_T\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0236\_a\_\_letter\_T\_.png}}

\textbf{Fig0503 \_original\_pattern\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0503 \_original\_pattern\_.png}}

\textbf{FigP0501.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0501.png}}

\textbf{Fig1218\_airplanes\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig1218\_airplanes\_.png}}

\textbf{Fig0534\_a\_\_ellipse\_and\_circle\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/Fig0534\_a\_\_ellipse\_and\_circle\_.png}}

\textbf{FigP0616\_a\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0616\_a\_.png}}

\textbf{FigP0918\_b\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0918\_b\_.png}}

\textbf{FigP0528\_c\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0528\_c\_.png}}

\textbf{FigP0528\_a\_\_single\_dot\_.png}

\includegraphics[scale=0.20]{{./dip3e\_masks/FigP0528\_a\_\_single\_dot\_.png}}
